Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-08 docs/google-research-awards-latam/main.tex
organizing template

%\title{Debugging I/O Anomalies in Distributed Configurable Systems}
\title{\LARGE{}Testing for Configuration Errors in Distributed Systems}
\author{}
\date{}

@@

\vspace{-2ex}
\small
\begin{table}[h!]
  \centering%% Centro de Inform\'atica - CIn \\
  \begin{tabular*}{.85\linewidth}{@{\extracolsep{\fill}}ll}
    PI: Marcelo d'Amorim (\url{damorim@cin.ufpe.br}) & Universidade Federal de Pernambuco \\
    Phone: +55 (81) 98800-2010 [mobile]  & Av. Jornalista Anibal Fernandes, S/N \\
    \phantom{x}\hspace{7ex}+55 (81) 2126-8430, ext. 4379 [work] & Cidade Universit\'aria, PE, Brazil, 50.740-560\\
    \multicolumn{2}{l}{\noindent\textbf{Contact}: Wei Jin
      (\url{superbobo@google.com})~~--~~\textbf{Sponsor}: Sai Zhang (\url{saizhang@google.com})}\\
  \end{tabular*}
\end{table}
\normalsize

\vspace{-2ex}
\begin{abstract}
This proposal focuses on the important problem of testing for
configuration errors in distributed systems. The goal is to increase
system's reliability by preventing these errors to escape to
production.
%% The input of our approach is a configurable distributed
%% program and the output is a set of constraints denoting what
%% configurations are likely valid for use.
\end{abstract}

%% Diagnosing those errors
%% can be very challenging.
%% The overall goal is to improve developer's productivity in fixing
%% those errors.  The input to our proposed approach is a set of
%% distributed traces and the output is a likely explanation of failure
%% that developers can relate.

@@

\Comment{Configurability enables developers to adapt
system's behavior to different circumstances.  by selecting or
  adjusting options. These systems are \emph{prevalent}. The
  Firefox web browser~\cite{firefox-web}, the Linux
  kernel~\cite{linux-kernel-web}, the GCC compiler
  infrastructure~\cite{gcc-web}, and the deals-recommendation web
  service Groupon~\cite{groupon-web} are some well-known examples of
  configurable systems. }

Configurable systems are those that can be adapted from a set of input
options, reflected in code in the form of variations. Configurable
systems are
prevalent\Comment{~\cite{yin-etal-sosp2011,weiss-etal-ase2017}} and,
unfortunately, configuration-related errors are difficult to
detect~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}
and diagnose~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014}.
Testing and debugging becomes even worse when the system being
configured is a distributed system~\cite{matt-welsh-blog}. Detecting
these errors with testing, before they escape, is therefore important
as it is hard to troubleshoot error manifestations in complex
production
environments~\cite{jin-orso-icse2012}. Configuration-related errors in
distributed systems are unfortunately \emph{not rare}. Some of these
errors have been widely publicized in the media given the volume of
users or data they affected~\cite{azure-error,facebook-error,
  dns-misconfiguration}.

%% Troubleshooting distributed systems is known to be
%% challenging~\cite{BeschastnikhWBE2016}\Comment{ as reconstructing the
%%   global state of the system after failure observations is difficult
%%   or even impossible~\cite{mattern-virtual-time89}}.
%% Distributed systems are prevalent. Examples of distributed
%% applications include the Google Spanner distributed
%% database~\cite{corbett-etal-osdi2012} and IoT
%% deployments~\cite{android-things-one}.

%% Configuration is an orthogonal aspect to distribution but one that
%% makes testing and debugging even more
%% challenging~\cite{matt-welsh-blog}.

\vspace{-1ex}
\begin{center}
\fbox{
  %  \begin{minipage}{18.75cm}
  \begin{minipage}{11.75cm}
    \centering
    \textit{The goal of this project is to improve reliability in
      distributed systems\\ by finding configuration errors during
      testing.}
  \end{minipage}
}
\end{center}
\vspace{-1ex}

%% These errors emerge from the inability of developers to anticipate the
%% impact of local changes in dependent
%% features~\cite{ribeiro-etal-icse2014}.
%% Configuration errors are even
%% more problematic when they manifest in distributed
%% systems.
%% Fighting configuration errors
%% is also
%% challenging~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,kim-etal-fse2013,ribeiro-etal-icse2014,behrang-etal-fse2015}.

%% Preventing developers from
%% making these
%% errors~\cite{kenner-etal-fosd-2010,spllift,brabrand-2012,ribeiro-etal-icse2014,behrang-etal-fse2015},
%% testing for these errors~\cite{cohen-etal-icse2003,cohen:issta07,cohen-shmuelur-icse2010,emine-etal-issta2011,medeiros-etal-icse2016}
%% and diagnosing those
%% errors~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014} are
%% challenging activities.
%% At Google, configuration errors are also a
%% problem.
%% Understanding these errors in complex distributed system is an
%% essential time-consuming activitiy~\cite{matt-welsh-blog}.

%\section{Related Work}

\vspace{1ex} \textbf{Related Work.}~Literature on distributed
debugging is vast~\cite{BeschastnikhWBE2016}. Record and replay
solutions, such as Friday~\cite{geels-usenix2007} and
D3S~\cite{d3s-debugging-deployed-distributed-systems}, capture
nondeterministic events during execution to replay them a posteriori.
Tracing solutions~\cite{sambasian-etal-techreport2014}, such as Pivot
Tracing~\cite{mace-etal-usenix2016}, instrument the application to
forward tracing metadata to a distributed database for offline
analysis. In principle, these solutions could be adapted to track
configuration data but they are either heavyweight or intrusive
(\ie{}, they require modification in software).  These issues limit
the applicability of Record and Replay and Tracing in practice. Log
Analysis does not suffer from these limitations as it mines anomalies
from the logs that the system already produces~\cite{xu-etal-slam10}.
However, Log Analysis needs to cope with the potential for missing
relevant data and also to handle massive amounts of data.
%%
Considering the configuration dimension, testing and debugging for
distributed systems has not been studied in
depth~\cite{matt-welsh-blog}, in contrast to what has been observed in
non-distributed
systems~\cite{yin-etal-sosp2011,zhang-ernst-icse2013,zhang-ernst-icse2014,behrang-etal-fse2015,weiss-etal-ase2017}.
Most testing in distributed systems is done manually and after the
fact (\ie{} after failures are observed) to augment regression test
suites~\cite{beschastnikh-etal-icse2014}. Model checking distributed
systems (,which is essentially systematic testing) has been
proposed~\cite{killian-etal-nsdi07,yang-etal-nsdi09} but these
existing approaches do not take configurations into account.

%% \section{Goal}
%% Our general goal is to improve system's reliability\Comment{ in distributed
%%   systems}.  Our specific goal is to find configuration errors in
%% distributed systems.

%% They are hard to diagnose, especially in distributed systems.
%% Furthermore, these errors gain importance when they relate to data
%% from large organizations or a large number of users.
%% Defects that escape to production still need to be handled and,
%% certainly, these are the cases that require more immediate
%% diagnosis.

%% ``In-production'' errors are inevitable; they originate from the
%% inherent inability of ``in-house'' testing to find all possible
%% bugs~\cite{jin-orso-icse2012}.  These errors are pressing given the
%% imminent impact on users.

%% We refer to this problem, prevalent in configuration error diagnosis,
%% as (configuration) error classification.

%% A common problem in
%% this context is to decide whether a failure was manifested because of
%% a misconfiguration, because of invalid inputs\Comment{Undocumented
%%   preconditions in code can delay observation of failures.}, or
%% because of software
%% bugs~\cite{zhang-ernst-icse2013,zhang-ernst-icse2014,sabrina-etal-splc15}.

\section{Approach\Comment{Solution Design (Error Classification from
    Distributed Traces)}}

We propose an approach that uses automated test generation to find
configuration errors in distributed systems.  Our approach exercises
the system observing anomalies in behavior due to configuration
changes. Testing configurable software is a topic on which the group
of the PI has focused in the recent
past~\cite{kim-etal-fse2013,souto-etal-splc2015,souto-etal-icse2017,souto-damorim-jss2017}.
Our approach is similar in spirit to MoDist~\cite{yang-etal-nsdi09}, a
black-box model checker that runs the system modifying certain aspects
during execution such as processor speed and message sequencing, but
it takes configuration options into account.

\vspace{1ex}\noindent\textbf{Input/Output.}~The input of our technique
is a configurable distributed system and the output is one of more
failing tests and error reports.

%% The input to our
%% problem is a set of distributed traces (\eg{}
%% using Dapper~\cite{dapper-google-tr2010}, Pivot tracing~\cite{mace-etal-usenix2016}), which collectively
%% indicate a failure manifestation.  The output is a high-level report
%% explaining the potential cause of failure.  For example, ``service Y

\vspace{1ex}\noindent\textbf{Requirements.}~The technique should be
simple to use and highly automated. It should produce high-level
reports that enable developers to promptly understand and fix the
problems identified. It should run efficiently.

%%   It should
%% leverage available data\Comment{~--~produced with widely-used
%%   tools~--~} as opposed to relying on additional data that could be
%% produced with new tools.

%% \begin{itemize}
%%    \setlength\itemsep{0.01em}    
%% \end{itemize}

%% As for (1), large distributed systems often provide monitoring
%% solutions to assist with bug triage.  This work will use the
%% distributed traces produced by Dapper~\cite{dapper-google-tr2010}, the
%% distributed tracing infrastructure at Google.

\newcommand{\taskvirtualization}{1}
\newcommand{\taskteststrategies}{2}
%\newcommand{\idinteractions}{3}
\newcommand{\idminimization}{3}

\vspace{1ex}\noindent\textbf{Tasks}.~\taskvirtualization{}) Define
containerization strategy. \taskteststrategies{}) Define test
strategy. \idminimization{}) Minimize test sequences.

%% \idinteractions{}) Identify interactions between configured
%% services.

%% \begin{enumerate}
%%   \setlength\itemsep{0.01em}
%% \item\label{task-virtualization} Define containerization strategy.
%% \item\label{task-test-strategies} Define test strategy.
%% \item\label{id-interactions} Identify interactions between configured services.
%% \item\label{id-minimization} Minimize test sequences.
%% %\item Create benchmark of configuration errors in distributed systems
%% \end{enumerate}

%\vspace{1ex}\noindent\textbf{Approach}.

\vspace{1ex} Considering task~\taskvirtualization{}, it is important
to start a distributed system quickly and to run the system in an
isolated environment. We plan to use Docker images~\cite{docker} to
jump start the individual nodes of a distributed system. Considering
task~\taskteststrategies{}, our approach is to use lighter weight test
methods first and then assess effectiveness and cost of heavier weight
testing strategies.  More specifically, initially, we plan to use
existing test cases~\cite{maddox-2015-acmqueue} and select
configurations to run those tests using black-box techniques, such as
Combinatorial Interaction Testing
(CIT)~\cite{nie-leung-acm-surveys2011}.  It is worth noting that
centralized configuration servers such as
ZooKeeper's~\cite{apache-zookeeper} and Spring Cloud
Config~\cite{spring-cloud-config} are becoming popular to manage
configurations in distributed systems and should facilitate this task.
We also plan to explore gray-box techniques for selecting
configurations~---~we will investigate the effectiveness of mining
network interactions to decide what configurations to test
next. Existing log analysis tools can help on
that~\cite{mace-etal-usenix2016}. For example, our analysis may
discover that a datum in a message triggers a different decision in a
node, as observed from execution logs, and that that datum is related
to a configuration option. We conjecture that selecting configurations
that triggers different interactions increases the ability of testing
to find faults. Finally, automated test generation can create
arbitrarily long test sequences which hinders reproducibility and
fault diagnosis.  Task~\idminimization{} is concerned with the
minimization of fault-revealing tests to facilitate debugging.

%% messages on the network, similarly to
%% MoDist~\cite{yang-etal-nsdi09}\Comment{ and
%%   Basset~\cite{lauterburg-etal-fse2010},}, but also by modifying
%% configurations.

We will build tools that implement and support our approach.  The
output of our approach is a failing test, which could reveal a bug or
a misconfiguration. In case the developer finds out that the failure
corresponds to a bug, the code needs to be fixed.  In case of
misconfigurations, our approach could be used to prevent errors
provided that the developer adds checks to (in)validate certain
configurations from being triggered.  Alternatively, the approach
could be used to diagnose errors as logs reporting error
manifestations could be saved and then used for comparison with
production runs.

%% Our first course of action to
%% diagnosing configuration errors is to search for unexpected
%% \emph{feature interactions}~\cite{pamela-zave-feature-interaction}.  A
%% feature interaction happens, for example, when a service reads from
%% the state that another service writes. The hypothesis is that the
%% failure was caused by an interaction across distributed services
%% manifested through a configuration that has not been extensively
%% tested, resulting in a failure.\Comment{ Consequently, the defect was
%%   enabled in production only at the point in time the error was
%%   manifested.}  As it is challenging to detect those interactions
%% without sacrificing system's performance (\eg{}, adding monitoring probes), we plan to use existing
%% execution logs to estimate them. To fix the problem, a developer needs
%% to either fix a bug in code related to that configuration or prevent
%% the use of that configuration, as it could be illegal.  In case no
%% discrepancy has been found in the patterns of configuration
%% interaction, our approach would look for anomalies in the use of input
%% data involving those configurations. Potential activities associated
%% to this project include:

%% \begin{itemize}
%%   \setlength\itemsep{0.01em}  
%%   \item Identify interaction between configured services.  This task
%%     is responsible to find what services interact
%%     and through which configurations they interact.  Existing log
%%     analysis tools can help assist this
%%     activity~\cite{beschastnikh-etal-icse2014,BeschastnikhWBE2016,shiviz-web}.
%%   \item Investigate techniques to precisely and efficiently identify
%%     anomalies in usage of input data, modulo service interaction and
%%     their configurations.  Potential solutions include the use of
%%     invariant detectors (e.g.,
%%     Daikon~\cite{daikon-2016,BeschastnikhWBE2016}) and anomaly
%%     detectors based on regression and neural network
%%     models~\cite{Alpaydin:2010:IML:1734076}, for instance.
%%   \item Create a benchmark of distributed systems with configuration
%%     errors.\Fix{elaborate...}
%%   \item 
%% \end{itemize}

%% This proposal addresses the problem of debugging large-scale
%% configurable distributed systems.  The hypothesis is that system's
%% configuration errors are often manifested through anomalies in I/O
%% usage.

%\subsection*{Details}

%% For the sake of presentation, we use the term ``test case'' to refer
%% to a scenario of execution that manifests a problem.  A test case can
%% be materialized through an executable test artifact (in-house) or
%% through an execution log (in-production).  Handling in-house and
%% in-production bugs are in the scope of this project.

%% Our debugging approach is summarized as follows: (1) Augment test
%% cases with differential test oracles, (2) Explore configurations from
%% the test, and (3) Look for correlations between configuration options
%% and failures.  We detail below each of these parts.

%% \textbf{Oracles (1).} We assume that an important class of errors in
%% distributed systems are due to
%% misconfigurations~\cite{matt-welsh-blog}.  Furthermore, we conjecture
%% that an important class of these errors manifest I/O anomalies (e.g.,
%% excessive use of memory or time).  We plan to apply differential
%% testing in this context to discover these problems.  More
%% specifically, we want to detect anomalies in the profile of resource
%% usage (memory/network) across multiple executions induced by a
%% selection of configurations over a given test.

%% \textbf{Configuration selection (2).} Testing is an essential part of
%% the debugging process. Test case diversity is generally considered
%% beneficial to identify root causes of
%% failure~\cite{campos-etal-ase2016}.  Diversity of configurations, in
%% particular, plays an important role in the context of this project.
%% We plan to use existing configuration selection
%% techniques~\cite{medeiros-etal-icse2016,kim-etal-fse2013,sabrina-etal-splc15,souto-damorim-jss-2016},
%% including ours, to explore the space of configurations reachable from
%% existing test cases.

%% \textbf{Fault localization and explanation (3).} Statistical-based Fault
%% Localization (SFL) is a lightweight method to identify suspicious
%% components in a computational system from a set of passing and failing
%% executions~\Fix{cite}.  We plan to apply SFL and look for abstractions
%% of error explanation that can be given to users to help identify the
%% culprit.

%% It is important to note that if executable test cases can be
%% obtained diagnosis can be performed at source-level.

%% \subsection*{Debugging in production}

%% In principle, the approach presented above could be used to identify
%% inconsistencies in existing integration tests, by exploring more
%% rigorously reachable configurations from tests.  However, defects that
%% escape to production still need to be handled and, certainly, these
%% are the cases that require more immediate diagnosis.  To this end, one
%% important challenge is to reconstruct, from production logs, the steps
%% that approximately characterize the original error-manifesting
%% execution.  Two alternatives for that will be investigated: (1) to
%% reconstruct executable integration tests that partially reflect the
%% observed behavior in logs.  This assumes that an infrastructure for
%% isolated re-execution of tests exists, which may not be realistic. (2)
%% to elaborate abstract behavior models for resource consumption which
%% \emph{are aware of configuration options used}.  Each approach is
%% challenging.

%% \Fix{...talk about surrogate regression + neural network models...}

%% Ideally, we would like even to generate new execution scenarios
%% from observations...

%% \subsection*{Future}
%% One potentially promising direction to expand this project is to use
%% historical data (both short and long-term) to prune the search space.
%% Lightweight change impact analysis can help finding hot spots for
%% analysis and code stability analysis can help finding cold spots.
%% Other directions for further investigation include plugin validation
%% for user-configurable applications (such as web browsers) and lifting
%% dataflow analysis for configuration awareness, a problem that has been
%% recently investigated but is restricted to simple
%% analysis~\cite{spllift}.  Recent advances of Datalog
%% solvers~\cite{ceri-etal-ieee-tkde-1989} should enable
%% declarative/flexible, yet efficient, specifications.

%% \subsection*{Plan}
%% The first activity in this project is to better understand the context
%% of application (e.g., nature of errors in the software under analysis)
%% as it will certainly drive important decisions in the solution design.
%% Validating our techniques (directly or not) on Google software is
%% ideal.

%% \section{Related Work}
%% \Fix{...general comments...}\Fix{...highlight Wei's BugRedux and Brum's Perfume.}

%% Because of the combinatorial blowup caused by the increasing number of
%% options in a large codebase, exhaustively testing all possible
%% configurations is prohibitive.

\section{Case Studies}

%% https://github.com/ibm-cloud-architecture/refarch-cloudnative-netflix
%% https://github.com/fernandoabcampos/spring-netflix-oss-microservices
%% https://github.com/jbossdemocentral/coolstore-microservice
%% https://github.com/robhinds/microservices
%% https://github.com/spencergibb/oscon2015
%% https://github.com/jduranmaster/MicroServices-Architecture-POC-Engine-SpringBoot-NetflixOSS
%% https://github.com/szokebarnabas/twitterminer

We plan to evaluate our approach in some of the following scenarios:

\begin{itemize}
  \setlength\itemsep{0.01em}
\item \textbf{Software-Defined Networking (SDN).} SDN is a network
  architecture that enables network administrators to programmatically
  control the network behavior through well-defined interfaces such as
  OpenFlow~\cite{open-networking}. Humans can make mistakes in an SDN
  as in any other configurable software.  For example, it is possible
  that ``one of the switches is sending packets to the wrong
  destination network''~\cite{scott-etal-nsdi2015}.
\item \textbf{Internet of Things (IoT).} IoT deployments are highly
  configurable and typically depend on services distributed on the
  network. This is the case for both cloud and non-cloud based IoT
  setups. Considering the scenario of a smart home, for example, the
  number of sensors and the configuration options on each sensor can
  vary (e.g., the max amount of smoke
  acceptable\footnote{~https://diyhacking.com/iot-smoke-alarm-arduino-esp8266-gas-sensor/}
  before signaling an alarm or sending a message to the apartment
  owner).  To note that the PI is involved in a Brazil-US cooperation
  project\footnote{~Funded by RNP, in Brazil, and NSF, in the
    US:~\url{https://www.nsf.gov/pubs/2017/nsf17024/nsf17024.jsp}}
  related to testing IoT infrastructures and this could create
  synergies that will help the project to succeed.

\item \textbf{Microservices.} Microservices is an increasingly-popular
  approach to organize applications (typically, web apps). It promotes
  the breakdown of code in small service units\Comment{ that
    communicate through lightweight protocols}. Consider, for example,
  the scenario where a monolithic application is refactored to use
  microservices. Refactorings can be buggy and the new channels
  created for communication (among microservices) can be vulnerable to
  attacks. 
  %http://mp.binaervarianz.de/pldi2017.pdf
%%  \item \textbf{Collaborative Apps}
\end{itemize}

%% \Comment{We consider using Open Source
%%     Software (OSS) that uses popular frameworks (e.g., Spring
%%     Cloud~\cite{spring-cloud}).}
%% to enable continuous delivery and deployment of
%%   applications.  Microservices promote

We are also eager to evaluate the techniques we develop in scenarios
within Google

@@

\section{Budget}

The project will support one PhD student for one year.  The total
budget for this period is 25,800 USD.

\begin{itemize}
  \setlength\itemsep{0.05em}  
\item Student salaries: 22,800 (=1,900*12)
\item Conference travel: 3,000
\end{itemize}

%% \begin{thebibliography}{99}
%% \bibitem{gonzalez2012} Jonay I. Gonz\'{a}lez Hern\'{a}ndez, 
%% Pilar Ruiz-Lapuente,	
%% Hugo M. Tabernero,	
%% David Montes,	
%% Ramon Canal,	
%% Javier M\'{e}ndez	
%% and Luigi R. Bedin,
%% {No surviving evolved companions of the progenitor of SN1006},
%% Nature, {\bf 489}, 533-536 (2012).
%% \end{thebibliography}

%\scriptsize
\footnotesize
\bibliographystyle{plain}
\bibliography{tmp}

@@

%%  LocalWords:  d'Amorim Universidade de Pernambuco UFPE Centro CIn
%%  LocalWords:  atica Jornalista Fernandes Cidade Universit Sai GCC
%%  LocalWords:  Zhang Configurability Groupon combinatorial codebase
%%  LocalWords:  tmp misconfigurations SFL dataflow Datalog BugRedux
%%  LocalWords:  Brum's misconfiguration Daikon IoT nondeterministic
%%  LocalWords:  posteriori metadata MoDist postmorten virtualization
%%  LocalWords:  pre USD startup ZooKeeper's Config SDN SDNs OpenFlow
%%  LocalWords:  programmatically Microservices Refactoring OSS Jin
%%  LocalWords:  reproducibility RNP refactored microservices
%%  LocalWords:  Refactorings

>>>>

\title{Finding Bugs in JavaScript Engines with Differential Testing}
\author{}
\date{}

@@

\vspace{-2ex}
\small    
\begin{table}[h!] 
  \centering%% Centro de Inform\'atica - CIn \\
  \begin{tabular*}{.85\linewidth}{l}

    Marcelo d'Amorim and Igor Sim\~oes (M.Sc. student)\\

    Postal Address: Av. Jornalista Anibal Fernandes, S/N. Cidade
    Universit\'aria, PE, Brazil, 50.740-560 \\

    Email addresses: \{damorim, isol2\}@cin.ufpe.br\\

    Phones: +55 (81) 2126-8430,
    ext. 4379 [work], +55 (81) 98800-2010 [mobile]\\

    Affiliation: Federal University of Pernambuco, Department of
    Computer Science.\\

    Contacts at Google:~\Fix{...}

  \end{tabular*}
\end{table}
\normalsize

\vspace{-2ex}
\begin{abstract}
...
\end{abstract}

@@

\Fix{...}

\vspace{-1ex}
\begin{center}
\fbox{
  \begin{minipage}{11.75cm}
    \centering
    \textit{...}
  \end{minipage}
}
\end{center}
\vspace{-1ex}

\vspace{1ex} \textbf{Related Work.}~\Fix{...}~\cite{maddox-2015-acmqueue}

\section{Design}

...

\vspace{1ex}\noindent\textbf{Input/Output.}~...

\section{Current Results}

\Fix{list/describe/explain some of the bugs we found here}

@@

\footnotesize
\bibliographystyle{plain}
\bibliography{tmp}

@@
